Untitled

### 2018-07-15 PaperCode.Rmd
Final LADS
Added in lads that had been received but not included. Total LADS 114. upgraded kingston and Wandsworth to LSOA from ward level

98nmol/L

@@

@@

Should type B be included? or just type A?

What's the Deal with Westminster?
Westminsters Data is very low, I want to check what codes are going on.
Westminster
PCLB00: Second home class B/A
PCLB50: 
PCLC00: Empty and unfurnsished
PCLC99: 
PCLD00: Undergoing major repairs
PCLJ50:
Single:

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
source(file.path(CommonCode, "AuxdataLoad.R"))
```

@@

@@

##Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

@@

#they deleted the classes
SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

@@

#Brightong and Hove

@@

@@

@@

WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure

#Kingston

KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure

@@

#number of LUPS and Total Homes
DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLADs = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           PercLADs = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length()),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           PercPop = Population/sum(EW2$Pop)) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

@@

PlotMap(BexleyLONDATA)

@@

#Analyse Boostrap

```{r}
test <- BootStrapRESExO$WestminsterLON%>% 
  group_by(class) %>%
  summarise_all(funs(mean))

@@

test <- BootStrapRESExO %>% 
  bind_rows %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")) )

@@

test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs", 
          y = "% difference from expected")
SaveFig("PricediffAllData.pdf")

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valuerat HounslowLONDATA <- read_excel("Hounslow Discounts - Bourne Info -210817.xls" )io>1)) + geom_point()

@@

EnglandCompTab <- EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

@@

xtable(EnglandCompTab, caption="Summary of effecrt across England",
       label = "tab:EnglandCompTab") %>% 
  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))

@@

Big Stats
```{r}

>>>>

new article and paper on airbnb effecr
https://www.citylab.com/equity/2018/03/what-airbnb-did-to-new-york-city/552749/?utm_source=atlfb

@@

Intellectual property rights and
disclosures under the Freedom of
Information Act

16. It may not be apparent to recipients that the information is
protected by copyright. Therefore when a public authority
wishes to protect its own copyright, or the copyright is owned
by a third party, it should advise the applicant that the
information remains copyright protected.

Please can you provide excel the file sent to Jonathan Bourne on xxx

The reference number for this case is xxx.

Yours faithfully,

Jonathan Bourne

@@

#OGL licence claim

All data used in this paper is covered by the Open Government Licence.

The Data meets all 4 criteria described in section 56 of "Datasets (sections 11, 19 & 45)" FOI guidance document.
These criteria are that the data is held by the authority, The data is part of a relveant copyright work (The data is held in a databse), the authority holds the copyright to the data (The information in the database is owned by the local council). 
As local authorities are public sector bodies (shown in the public sector classification guide) and that council tax is a core task, normally the data would be covered by the RPSI. However, following section 5 of the Re use of public sector infrmation regulations 2015.

"5.—(1) These Regulations do not apply to a document where—

(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review; or""

As the document the councils needed to complete is custom made and not part of the public task, the RPSI does not cover the resultant work and licencing reverts to the FOIA. 
The FOIA states that a specific licence must be given for all datasets released under the act. As no charge has been levied against the use of the data then the default Open government licence is applied following section 69 of the "Datasets (sections 11, 19 & 45)" FOI guidance document.

@@

Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Figures" #file.path(basewd, "Figures")
TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
source(file.path(CommonCode, "AuxdataLoad.R"))

@@

DudleyDATA <- read_excel("Completed DudleyDiscountsLSOA.xlsx"  )[1:4] %>%  
  StructureData()

@@

##Norfolk
```{r}
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

@@

SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

NorwichDATA <- read_excel("Norwich Discounts FINAL.xlsx"  , sheet=1)[1:4] %>%
  StructureData(2:8)

@@

#South East

@@

ValeWhiteDATA <- read_excel("Vale of White HorseDiscountsLSOA (00000002).xlsx" , sheet=1)[1:4] %>%
  StructureData(c(5,7,8,9,10,14))

SouthOxfordDATA <- read_excel("South OxfordshireDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(c(5,7,8,9,10,14))

@@

WakefieldData <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
  StructureData(2:7)

@@

# WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
#   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
#   arrange(`Ptc Wardname`) %>% 
#   filter(!is.na(`Ptc Wardname`)) %>% 
#   bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
#               select(Admin_ward_code)) %>%
#   mutate(LowUse = Empty) %>%
#   SemiDataStructure
# 
# 
# #Kingston
# 
# KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
#   arrange(X__1) %>% slice(1:16) %>%
#   bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
#               select(Admin_ward_code)) %>%
#   mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
#   SemiDataStructure

@@

#number of LUPS and Total Homes
DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           'LADs' = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
           '% of all LADs' = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length())*100,
           LUPs = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           '% of all Homes' = Homes/sum(EW2$Homes)*100,
           Population = sum(Pop, na.rm= T),
           '% of total population' = Population/sum(EW2$Pop)*100) %>%
  mutate_if(.<1, funs(signif(.,3))) %>%
  mutate_if(.>1, as.integer) %>%
  mutate_all(as.character) %>% 
  gather

@@

PlotMap(WandsworthLONDDATA)

@@

#Analyse Bootstrap

```{r}
test <- BootStrapRESExO$WestminsterLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean))

@@

test <- BootStrapRESExO %>% 
  bind_rows %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
               LUPmore = RatioExvsAct>1)

@@

test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs")
SaveFig("PricediffAllData.pdf")

#Total value of homes and LUPS

BootStrapRESExO2 <- BootStrapRESExO %>% map(~.x %>% ungroup)

LADnames <- names(BootStrapRESExO)

LUPval <-   map2(.x =BootStrapRESExO2, .y =   names(BootStrapRESExO2),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)

LUPval$VancouverTax %>% sum(.)/1000

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

@@

EnglandCompTab <- EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes)*100,
         PopPerc = Pop/sum(Pop)*100) %>%
  rename('LUPs>Homes' = Comp.Type, 
         Population = Pop,
         'Homes %' = HomesPerc,
         'Population %' = PopPerc) %>%
  gather(key = "key", "value"= value, -"LUPs>Homes") %>%
  mutate(value = value %>% round %>%as.integer) %>%
  spread(key = "LUPs>Homes", value = value)

@@

xtable(EnglandCompTab, caption="Summary of effect across England",
       label = "tab:EnglandCompTab") %>% 
  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))

@@
